Supplementary Content for the article *The role of functional diversity in ecosystem regime shifts*

### 2022-05-31 experiments/2_supplement/supplement.Rmd
Move Fig 5 from figures_main_ms.R to Supplement

>>>>

# Previously figure 5 Main Manuscript
```{r fig_5_log, echo = FALSE,  include=TRUE, fig.cap='Previously figure 5 Main Manuscript log', fig.height=8, fig.width=8, fig.align="center"}
## Figure 5 ----
## Assessing additivity of diversity effect sizes
## By Uriah
## Owen switched to SB_tot

all_stab_results_small <- readRDS(here("data/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method.RDS"))

wait_time <- 1e6
all_stab_results9 <- all_stab_results_small %>%
  distinct() %>%  #there are some duplicated rows....? yes, some treatment combs were repeated when sub1 was made
  filter(num_strains == 9,
         Species == "SB_tot",
         waittime == wait_time)

all_stab_results9 <- all_stab_results9[with(all_stab_results9, order(var_treat, var_gmax)),]

all_stab_results9$method <- "Simulated"

### Things used for plotting ----

### Fig 5 - log ----

agg_stab_strain9 <- combine_fct("EF_log")

agg_stab_strain9_temp <- agg_stab_strain9 %>%
  dplyr::filter(var_treat=="CB-SB-PB")

agg_stab_strain9 <- agg_stab_strain9 %>%
  dplyr::filter(var_treat!="CB-SB-PB")

agg_stab_strain9 <- rbind(agg_stab_strain9,
                          agg_stab_strain9_temp %>% filter(method %in% c("CB+SBPB","Simulated")) %>% mutate(var_treat="CB-SB-PB & CB+SBPB"),
                          agg_stab_strain9_temp %>% filter(method %in% c("PB+CBSB","Simulated")) %>% mutate(var_treat="CB-SB-PB & PB+CBSB"),
                          agg_stab_strain9_temp %>% filter(method %in% c("SB+CBPB","Simulated")) %>% mutate(var_treat="CB-SB-PB & SB+CBPB"))

agg_stab_strain9 <- agg_stab_strain9 %>%
  mutate(method2 = ifelse(agg_stab_strain9$method=="Simulated","Simulated","Calculated")) %>%
  rename(Calculation=method, Method=method2)%>%
  mutate(Calculation = factor(Calculation, levels = c("Simulated","CB+SB","CB+PB","SB+PB",
                                                      "CB+SBPB","PB+CBSB","SB+CBPB")),
         Method = factor(Method, levels = c("Simulated","Calculated")))

# the legend
fig5legend <- agg_stab_strain9 %>%
  filter(Species == "SB_tot", num_strains==9) %>%
  ggplot(aes(x = stand_var, linetype=Method, col=Calculation)) +
  geom_line(aes(y = hyst_min_log), size = 1) +
  geom_line(aes(y = hyst_max_log), size = 1) +
  scale_color_manual(values = c("black","#e41a1c","#377eb8","#4daf4a","#984ea3","#ff7f00","#a65628")) +
  scale_linetype_manual(values = c(1,2))+
  coord_flip() +
  theme_bw() +
  theme(legend.position="right")

fig5legend <- ggpubr::get_legend(fig5legend)

# the y and x labels
# ylab <- ggplot(data.frame(l = "            Standardised amount of trait variation", x = 1, y = 4.1)) +
ylab <- ggplot(data.frame(l = "Standardised amount of trait variation", x = 1, y = 4.1)) +
  geom_text(aes(x, y, label = l), angle = 90, size=4.5) + 
  theme_void() +
  coord_cartesian(clip = "off")

xlab <- ggplot(data.frame(x = 1, y = 1)) +
  geom_text(aes(x, y), label = expression('log'[10]*"(oxygen diffusivity) (h"^{-1}*")"), size=4.5) + 
  theme_void() +
  coord_cartesian(clip = "off")

# colours and tags used
colours <- c(Simulated="black",`CB+SB`="#e41a1c",`CB+PB`="#377eb8",
             `SB+PB`="#4daf4a",`CB+SBPB`="#984ea3",`PB+CBSB`="#ff7f00",
             `SB+CBPB`="#a65628")

tags <- c(`CB`="a",`SB`="b",`PB`="c",
          `CB-SB`="d",`CB-PB`="e",`SB-PB`="f",
          `CB-SB-PB & CB+SBPB`="g",`CB-SB-PB & PB+CBSB`="h",`CB-SB-PB & SB+CBPB`="i")

# The figure

fig5_log <- split(agg_stab_strain9, f=agg_stab_strain9$var_treat, drop = T)

fig5_log <- lapply(fig5_log, function(df){
  tag <- tags[as.character(unique(df$var_treat))]
  plot <- df %>%
    filter(Species == "SB_tot", num_strains==9) %>%
    ggplot(aes(x = stand_var, linetype=Method, col=Calculation)) +
    geom_hline(yintercept = c(-8, 0), col = "black", linetype=3) +
    geom_line(aes(y = hyst_min_log), size = 1) +
    geom_line(aes(y = hyst_max_log), size = 1) +
    facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
    labs(y="Oxygen diffusivity\n[log10 uM per hour]",
         x="Amount of trait variation\n[see text for units]",
         linetype="Method",col="Calculation", tag=tag) +
    scale_color_manual(values = colours[unique(df$Calculation)]) +
    scale_linetype_manual(values = c(1,2))+
    coord_flip() +
    theme_bw()+
    theme(legend.position="none",
          axis.title = element_blank(),
          axis.ticks = element_blank(),
          axis.text = element_blank())

  if(tag %in% c("a","d")){
    plot <- plot + theme(axis.text.y = element_text(),
                         axis.ticks.y = element_line())
  }
  if(tag %in% c("h","i")){
    plot <- plot + theme(axis.text.x = element_text(),
                         axis.ticks.x = element_line())
  }
  if(tag == "g"){
    plot <- plot + theme(axis.text = element_text(),
                         axis.ticks = element_line())
  }
  plot
})

ylab + Reduce("+",fig5_log) + fig5legend +
  plot_spacer() + xlab + plot_spacer() +
  plot_layout(ncol = 3, heights = c(25,1), widths = c(1,21,3))

# ggsave(here("experiments/1_figures_main_ms/Figure_5_log.pdf"),
#        width = 8, height = 8)

```{r fig_5_linear, echo = FALSE,  include=TRUE, fig.cap='Previously figure 5 Main Manuscript linear', fig.height=8, fig.width=8, fig.align="center"}

### Fig 5 - linear ----

agg_stab_strain9 <- combine_fct("EF_lin")

agg_stab_strain9_temp <- agg_stab_strain9 %>%
  dplyr::filter(var_treat=="CB-SB-PB")

agg_stab_strain9 <- agg_stab_strain9 %>%
  dplyr::filter(var_treat!="CB-SB-PB")

agg_stab_strain9 <- rbind(agg_stab_strain9,
                          agg_stab_strain9_temp %>% filter(method %in% c("CB+SBPB","Simulated")) %>% mutate(var_treat="CB-SB-PB & CB+SBPB"),
                          agg_stab_strain9_temp %>% filter(method %in% c("PB+CBSB","Simulated")) %>% mutate(var_treat="CB-SB-PB & PB+CBSB"),
                          agg_stab_strain9_temp %>% filter(method %in% c("SB+CBPB","Simulated")) %>% mutate(var_treat="CB-SB-PB & SB+CBPB"))

agg_stab_strain9 <- agg_stab_strain9 %>%
  mutate(method2 = ifelse(agg_stab_strain9$method=="Simulated","Simulated","Calculated")) %>%
  rename(Calculation=method, Method=method2)%>%
  mutate(Calculation = factor(Calculation, levels = c("Simulated","CB+SB","CB+PB","SB+PB",
                                                      "CB+SBPB","PB+CBSB","SB+CBPB")),
         Method = factor(Method, levels = c("Simulated","Calculated")))

fig5_lin <- split(agg_stab_strain9, f=agg_stab_strain9$var_treat, drop = T)

fig5_lin <- lapply(fig5_lin, function(df){
  tag <- tags[as.character(unique(df$var_treat))]
  plot <- df %>%
    filter(Species == "SB_tot", num_strains==9) %>%
    ggplot(aes(x = stand_var, linetype=Method, col=Calculation)) +
    geom_hline(yintercept = c(-8, 0), col = "black", linetype=3) +
    geom_line(aes(y = hyst_min_log), size = 1) +
    geom_line(aes(y = hyst_max_log), size = 1) +
    facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
    labs(y="Oxygen diffusivity\n[log10 uM per hour]",
         x="Amount of trait variation\n[see text for units]",
         linetype="Method",col="Calculation", tag=tag) +
    scale_color_manual(values = colours[unique(df$Calculation)]) +
    scale_linetype_manual(values = c(1,2))+
    coord_flip() +
    theme_bw()+
    theme(legend.position="none",
          axis.title = element_blank(),
          axis.ticks = element_blank(),
          axis.text = element_blank())

  if(tag %in% c("a","d")){
    plot <- plot + theme(axis.text.y = element_text(),
                         axis.ticks.y = element_line())
  }
  if(tag %in% c("h","i")){
    plot <- plot + theme(axis.text.x = element_text(),
                         axis.ticks.x = element_line())
  }
  if(tag == "g"){
    plot <- plot + theme(axis.text = element_text(),
                         axis.ticks = element_line())
  }
  plot
})

ylab + Reduce("+",fig5_lin) + fig5legend +
  plot_spacer() + xlab + plot_spacer() +
  plot_layout(ncol = 3, heights = c(25,1), widths = c(1,21,3))

# ggsave(here("experiments/1_figures_main_ms/Figure_5_lin.pdf"),
#        width = 8, height = 8)
```
